\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-01-24 Latex/paper.tex
# last steps in convexity adjustment to cms
# new version paper

\subsection{CMSs}
We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, let us define
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}
We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$. Therefore
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
\end{equation*}
Then convexity adjustment for a CMS will be define as
\begin{equation}
CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
\end{equation} 
Now, after some changes of measure, it is easy to show that
\begin{equation}\label{expected_t_p_cms}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{equation}
where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
\begin{equation} \label{clark_ocone_swap_m}
M(T_a,T_p) = M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
\end{equation}
Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
\begin{align}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
&=  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right)
\end{align}

\begin{example}
In order to get a little bit of intuition we will use the last expression for the particular case of a Hull-White model. In this case, is easy to show that 
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
therefore we have that 
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} \partial_x S_{a,b}(s) \partial_x M(s,T_p) ds \right)
\end{equation*}
Now, if we apply again Clark-Ocone to $\partial_x M(s,T_p)$, we get that

\begin{align*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)}\int_{0}^{T_a} (D_s X_{T_a})^{2} ds \\
&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s} \partial^{2}_{x} S_{a,b}(u_1) \partial^{2}_{x} M(u_1,T_p) (D_{u_1}x_s)^{2}  du_1 ds \right)
\end{align*}
We must observe that, that it is easy to get an extra term in the expansion, only we must repeat the same argument that before, but now in $\partial^{2}_x M(u_1, T_p)$ we will get the next approximation

\begin{align*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &\approx S_{a,b}(0) + \frac{\partial_x S_{a,b}(0) \partial_x M(0,T_p)}{M(0,T_p)} \int_{0}^{T_a} (D_s X_{T_a})^{2} ds \\
&+ \frac{\partial^{2}_{x} S_{a,b}(0) \partial^{2}_{x} M(0,T_p)}{M(0,T_p)} \int_{0}^{T_a} (D_s X_{T_a})^{2} \int_{0}^{s}  (D_{u_1}x_s)^{2}  du_1 ds
\end{align*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor for the underlying swap is 5Y using the firt approximation and Monte Carlo method
\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.25]{Figures/cms_convexity_order_1.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}

\end{example}
Now, we will continue with the generic case. Follow the same idea, that in the last example, if we apply Clark-Ocone to $\partial_x M(T_a,T_p)$ we have that
\begin{equation*}
\partial_x M(T_a,T_p) = \partial_x M(0,T_p) + \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1}  
\end{equation*}
Therefore
\begin{align}\label{general_cms_approximatìon_first_step}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) &= S_{a,b}(0) + \frac{\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a)
\mathbb{E}^{01}_s\left(D_s x_{T_a} \right) ds\right) \\
&+ \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \partial_x S_{a,b}(T_a) D_{s} X_{T_a} \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1} ds \right)
\end{align}
Let us define
\begin{align*}
A(T_a) &= \frac{\partial_x M(0,T_p)}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{01}_s\left(D_s x_{T_a} \right) ds\right) \\
\epsilon(T_a) &= \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} \partial_x S_{a,b}(T_a) D_{s} X_{T_a} \int_{0}^{T_a} \mathbb{E}_{u_1}^{01}\left(D_{u_1} \partial^{2}_x M(T_a,T_p) D_{u_1} x_{T_a} \right) dW^{01}_{u_1} ds \right)
\end{align*}
If we use again Calrk-Ocone with $\partial_x S_{a,b}(T_a)$ we have that
\begin{equation*}
\partial_x S_{a,b}(T_a) = \partial_x S_{a,b}(0) + \int_{0}^{T_a} \mathbb{E}^{01}\left( \mathbb{E}^{01}\left( \partial^{2}_x S_{a,b}(T_a)\right) D_s X_{T_a}  dW^{01}_s  \right) 
\end{equation*}
Therefore
\begin{equation*}
A(T_a) =
\end{equation*}

>>>>

\subsection{CMSs}
We will define the swap rate from $T_a$ to $T_b$ at time $t$
\begin{equation*}
S_{a,b}(t) = \frac{\sum_{i=1}^{n_E}\delta_{t^{E}_{i-1}, t^{E}_i} L^{E}(t,t^{E}_{i-1}, t^{E}_{i}) P_{ois}(t,t^{E}_{i})}{01(t,T_a,T_b)}
\end{equation*}
where
\begin{align*}
01(t,T_a,T_b) = \sum_{j=1}^{n_f} \delta_{t^{f}_{i-1}, t^{f}_i} P_{ois}(t,t^{f}_{j}) \\
T_a=T^{E}_0 < T^{E}_i< \cdots < T^{E}_{n_E}=T_b \quad i=0,\cdots,n_E&  \\
T_a=T^{f}_0 < T^{f}_j< \cdots < T^{f}_{n_f}=T_b \quad j=0,\cdots,n_f&
\end{align*}
The same way, let us define
\begin{equation*}
S^{ois}_{a,b}(t) = \frac{P_{ois}(t,T^{E}_a) - P_{ois}(t,T^{E}_b)}{01(t,T_a,T_b)}. 
\end{equation*}
We suppose, that we have a flow in $T_a < T_p < T_b$ with value $S_{a,b}(T_a)$. We know that, $S_{a,b}(T_a)$ is a martingale under the measure $\mathbb{Q}^{01}$, but not under the measure $\mathbb{Q}^{T_p}$. Therefore
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \neq S_{a,b}(0).
\end{equation*}
Then convexity adjustment for a CMS will be define as
\begin{equation}
CA_{CMS}(T_p) = \mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) - S_{a,b}(0).
\end{equation} 
Now, after some changes of measure, it is easy to show that
\begin{equation}\label{expected_t_p_cms}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) = \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(S_{a,b}(T_a) M(T_a,T_p)\right)
\end{equation}
where $M(t,T_p)= \frac{P_{ois}(t,T_p)}{01(t,T_a,T_p)}$. Now ¡, if we apply Clark-Ocone formula to $M(T_a,T_p)$ we get that
\begin{equation} \label{clark_ocone_swap_m}
M(T_a,T_p) = M(0,T_p)+ \int_{0}^{T_a} \mathbb{E}_s^{01}\left(D_s M(T_a,T_p)\right) dW^{01}_s
\end{equation}
Then, if we sustitute the last expressions in (\ref{expected_t_p_cms}) we have that
\begin{align}\label{cms_first_order_convexity}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) =& S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left( S_a,b(T_a) \int_{0}^{T_a} \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) dW^{0,1}_s   \right) \nonumber \\
=&  S_{a,b}(0) + \frac{1}{M(0,T_p)} \mathbb{E}^{01}\left(\int_{0}^{T_a} D_s X_{T_a} \partial_x S_{a,b}(T_a) \mathbb{E}^{0,1}_s\left(D_sX_{T_a}\partial_x M(T_a,T_p)  \right) ds   \right) \nonumber \\
\approx&  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \mathbb{E}^{0,1}\left( \int_{0}^{T_a} \left(\mathbb{E}_s^{0,1}\left( D_s x_{T_a}\right)\right)^{2} ds  \right)
\end{align}

\begin{example}
In order to check the accuracy of the last approximation, we will compute with Monte Carlo method the exact value of $\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right)$ under spot measure $\mathbb{Q}$ i.e we will compute  $\frac{1}{P(0,T_p)}  \mathbb{E}^{\mathbb{Q}}\left(\frac{S_{a,b}(T_a)}{\beta_{T_a}} \right)$. In the case of a Hull-White model, we have that
$$
D_s x_{T_a} = \sigma \exp(-(T_a - s))
$$
therefore (\ref{cms_first_order_convexity}) is equal to
\begin{equation*}
\mathbb{E}^{T_p}\left(S_{a,b}(T_a)\right) \approx  S_{a,b}(0) + \frac{\partial_x S_{a,b}(T_a, \bar{x}_0(T_a),\bar{y}(T_a))\partial_x M(T_a,T_p, \bar{x}_0(T_a),\bar{y}(T_a))}{M(0,T_p)} \frac{\sigma^{2}(1-\exp(-2kT_a))}{2k}.
\end{equation*}
In the next figure, we can see the convexity adjustment for a CMS where the tenor of the underlying swap is 5Y using the last approximation and Montecarlo method with parameters for the Hull-White model $\sigma=0.01$ and $k=0.0007$

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.25]{Figures/cms_convexity_order_1.jpg}
		\caption{Convexity Mc Vs Convexity Malliavin}
	\end{center}
\end{figure}
